\documentclass[a4paper,12pt,dvipsnames]{letter}
%
\usepackage[a4paper]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{courier}
\usepackage{array}
\usepackage{booktabs}
\usepackage{amsmath} 
\usepackage{amsfonts} 
\usepackage{amssymb}
\usepackage{wasysym}
\usepackage{marvosym}
\usepackage{stmaryrd}
\usepackage{tikz}
\usepackage{textcomp}
\usepackage{enumitem}
%
% set page geometry
\geometry{top=0.5cm,left=1cm,right=4cm,bottom=1cm}
\pagestyle{empty}
%
% special columns
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
%
% increase row height
\renewcommand{\arraystretch}{1.0}
%
\makeatletter
\newcommand{\thickhline}{\noalign {\ifnum 0=`}\fi \hrule height 2pt \futurelet \reserved@a \@xhline}
\newcommand{\medhline}{\noalign {\ifnum 0=`}\fi \hrule height 1pt \futurelet \reserved@a \@xhline}
\newcolumntype{"}{@{\hskip\tabcolsep\vrule width 1pt\hskip\tabcolsep}}
\makeatother
%
\newlength{\Oldarrayrulewidth}
\newcommand{\Cline}[2]{\noalign{\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}}\noalign{\global\setlength{\arrayrulewidth}{#1}}\cline{#2}\noalign{\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}}}
%
% my commands
\newcommand{\rot}[1]{\textcolor{red}{#1}}
\newcommand{\blau}[1]{\textcolor{blue}{#1}}
\newcommand{\grun}[1]{\textcolor{Green}{#1}}
\newcommand{\rotb}[1]{\textcolor{red}  {\textbf{#1}}}
\newcommand{\grnb}[1]{\textcolor{Green}{\textbf{#1}}}
\newcommand{\blub}[1]{\textcolor{blue} {\textbf{#1}}}
\newcommand{\radio}[1]{\textcolor{blue}{#1}}
\newcommand{\call}[1]{\textcolor{blue}{{#1}}}
\newcommand{\button}[1]{\textbf{#1}}
\newcommand{\degC}{\textdegree{}C}
\newcommand{\Deg}{\textdegree{}}
\newcommand{\ok}[1]{\textcolor{Green}{\textbf{#1}}}
\newcommand{\warn}[1]{\textcolor{Red}{\textbf{#1}}}
\newcommand{\myHead}[1]{{\LARGE\textsc{\textbf{#1}}}}
\newcommand{\myhead}[1]{{\Large\textsc{\textbf{#1}}}}
% itemize
\renewcommand{\labelitemi}{{$\bullet$\;}}
\renewcommand{\labelitemii}{{$\bullet$\;}}
\renewcommand{\labelitemiii}{$\bullet$\;}
\renewcommand{\labelitemiv}{$\bullet$\;}
% color bullets
\newcommand{\bi}{\textcolor{ProcessBlue}{$\bullet$\;}}
\newcommand{\ri}{\textcolor{Red}{$\bullet$\;}}
\newcommand{\gi}{\textcolor{Green}{$\bullet$\;}}
\newcommand{\yi}{\textcolor{Yellow}{$\bullet$\;}}
\newcommand{\vi}{\textcolor{Plum}{$\bullet$\;}}
\newcommand{\mi}{\textcolor{Magenta}{$\bullet$\;}}
\newcommand{\oi}{\textcolor{Orange}{$\bullet$\;}}
\newcommand{\ai}{\textcolor{Apricot}{$\bullet$\;}}
\renewcommand{\ni}{\textcolor{Brown}{$\bullet$\;}}
%
\newcommand{\mr}[2]{\multirow{#1}{*}{#2}}
\newcommand{\mcl}[2]{\multicolumn{#1}{|c|}{#2}}
\newcommand{\tb}[1]{\textbf{#1}}
\newcommand{\tp}[1]{\textsf{#1}}
\renewcommand{\tp}[1]{\fontfamily{cmss}\selectfont #1}
\newcommand{\refn}{Ref.\,\fontfamily{ppl}\selectfont\#\fontfamily{cmss}\selectfont}
%
% some info
\pdfinfo{%
  /Title    (F-5E-3 Tiger II Procedures)
  /Author   (funkyfranky)
  /Creator  ()
  /Producer ()
  /Subject  ()
  /Keywords (F-5E, Tiger II, Kneeboard, Procedures)
}
%
%\item[] \myHead{Preflight Checks}
% Note: max 29 items per page
\begin{document}
\texttt{
% ------------------------------------------------------------------------------------------------------------------------------------------------
\begin{itemize}
 \item[] \myHead{Preflight Checks}
 \item If required, tell \radio{Chief} to \radio{PLACE the WHEEL CHOCKS}.
  %left console
 \item[] \tb{Left console:}
 \item[\mi] Circuit breakers\dotfill\button{CHECK}
 \item[\mi] Rudder trim knob\dotfill\button{CENTERED}
 \item[\mi] Radar mode selector\dotfill\button{OFF}
 \item[\gi] Throttles\dotfill\button{OFF}
 \item[\gi] Flap lever\dotfill\button{THUMB SW}
 \item[\gi] Flap thumb switch\dotfill\button{UP}
 \item[\gi] Speed brake switch\dotfill\button{NEUTRAL}
 \item[\gi] Nose strut switch\dotfill\button{RETRACT}
  % left vertical
 \item[]\tb{Left vertical:}
 \item[\bi] Fuel shutoff switches - left and right\dotfill\button{GUARDS CLOSED}
 \item[\bi] Armament light control knob\dotfill\button{AS REQUIRED}
 \item[\bi] Landing gear alternate release handlse\dotfill\button{FULLY STOWED}
 \item[\bi] Landing \& taxi light switch\dotfill\button{OFF}
 \item[\bi] Missile volume control\dotfill\button{FULLY COUNTERCLOCKWISE}
 \item[\bi] Armament and jettison switches\dotfill\button{OFF and SAFE}
 %\item External stores jettison handle\dotfill\button{IN}
  % instrument panel
 \item[]\tb{Instrument panel:}
 \item[\yi] Landing gear lever\dotfill\button{LG DOWN}
 \item[\yi] Drag chute handle\dotfill\button{IN}
 \item[\yi] Flight instruments\dotfill\button{CHECK and SET}
 \item[\oi] Optical sight mode selector\dotfill\button{AS REQUIRED}
 \item[\yi] Aux intake doors indicator\dotfill\ok{BARBER POLE}
  % pedestal
 \item[]\tb{Pedestal:}
 \item[\ai] UHF radio and frequency\dotfill\button{AS REQUIRED}
 \item[\ai] TACAN\dotfill\button{AS REQUIRED}
 \item[\ai] NAV MODE switch\dotfill\button{AS REQUIRED}
 \item[\ai] Antenna switch\dotfill\button{AS REQUIRED}
 \item[\ai] Circuit breakers\dotfill\button{CHECK}
\end{itemize}
% ------------ 
\newpage
% Preflight page 2
\begin{itemize} 
 % right vertical
 \item[] \myHead{Preflight Checks}
 \item[]\tb{Right vertical:}
 \item[\ni] Cockpit pressurization and temp.\;controls\dotfill\button{AS REQUIRED}
 \item[\ni] Anti-ice switch\dotfill\button{OFF}
 \item[\ni] External fuel transfer switches\dotfill\button{OFF}
 \item[\ni] Fuel boost pump switches\dotfill\button{LEFT and RIGHT}
 \item[\ni] Crossfeed switch\dotfill\button{OFF}
 \item[\ni] Auto balance switch\dotfill\button{CENTERED}
 \item[\ni] Canopy jettison T-handle\dotfill\button{IN}
 \item[\ni] Battery switch\dotfill\button{BATT}
 \item[\yi] Aux intake doors indicator\dotfill\ok{CLOSE} 
 \item[\ni] Generator switches\dotfill\button{L\;GEN and R\;GEN}
 % right console
 \item[]\tb{Right console:}
 \item[\ri] Oxygen system\dotfill\button{CHECK}
 \begin{itemize}
  \item[\ri] Supply pressure gage\dotfill\ok{65-110\;PSI}
  \item[\ri] Quantity indicator\dotfill\button{CHECK}
  \item[\ri] Supply lever\dotfill\button{ON}
  \item[\ri] Diluter lever\dotfill\button{NORMAL}
  \item[\ri] Emergency lever\dotfill\button{NORMAL}
 \end{itemize}
 \item[\ri] IFF/SIF\dotfill\button{STBY}
 \item[\ri] Fuel and oxygen check switch\dotfill\button{GAGE\;TEST and QTY\;CHECK}
 \item[\ri] Compass switch\dotfill\button{AS REQUIRED}
 \item[\ri] Internal and external lights\dotfill\button{AS REQUIRED}
 \item[\ri] Rotating beacon\dotfill\button{AS REQUIRED}
 \item[\ri] Light warning test switch\dotfill\button{TEST}
 \item[\ri] Circuit breakers\dotfill\button{CHECK}
 \item If required, tell \radio{Chief} to turn \radio{GROUND POWER ON}.
\end{itemize}
% ----------------------------------- 
\newpage
% Engine Start-up
\begin{itemize}
 \item[] \myHead{Engine Startup}
 \item Radio \radio{ATC} and \radio{REQUEST START-UP}.
 \item Tell \radio{Chief} to \radio{CONNECT GROUND AIR Supply} unit.
 \item Tell \radio{Chief} to \radio{APPLY GROUND AIR} to motor left engine.
 \item[\yi] When left engine RPM reaches 10\;\%
 \begin{itemize}
  \item[\gi] Left engine throttle\dotfill\button{IDLE}
  \item[\bi] Left engine start\dotfill\button{PUSH}
 \end{itemize}
 \item[\yi] Left engine should stabalize within 35 sec\dotfill\button{CHECK}
  \begin{itemize}
  \item[\yi] RPM\dotfill\ok{49-52\;\%}
  \item[\yi] EGT\dotfill\ok{>\,140\;\degC}
  %\item Nozzle position\dotfill\ok{60-79\;\%}
  \item[\yi] Nozzle position\dotfill\ok{70-80\;\%}
  \item[\yi] Fuel flow rate\dotfill\ok{\textasciitilde\,400\;pph}
  \item[\yi] Oil pressure\dotfill\ok{5-20\;psi}
  \item[\yi] Hydraulic pressure\dotfill\ok{2800-3200\;psi}
  \item[\ri] Generator caustion light\dotfill\ok{OUT}
  \item[\yi]Auxiliary intake doors indicator\dotfill\ok{BARBER POLE}
 \end{itemize}
 \item Tell \radio{Chief} to \radio{APPLY GROUND AIR} to motor right engine.
 \item[\yi] When right engine RPM reaches 10\;\%
 \begin{itemize}
  \item[\gi] Reft engine throttle\dotfill\button{IDLE}
  \item[\bi] Reft engine start\dotfill\button{PUSH}
 \end{itemize}
 \item[\yi] Right engine should stabalize within 35 sec\dotfill\button{CHECK}
 \item[\yi] Auxiliary intake doors indicator\dotfill\ok{OPEN}
 \item Tell \radio{Chief} to \radio{DISCONNECT GROUND AIR Supply} unit.
 \item If required, tell \radio{Chief} to turn \radio{GROUND POWER OFF}.
\end{itemize}
% --------------------------------------
\newpage
% Crossbleed start
\begin{itemize}
 \item[] \myHead{Crossbleed Start}
 \item Tell \radio{Chief} to \radio{DISCONNECT GROUND AIR Supply} unit.
 \item If required, tell \radio{Chief} to turn \radio{GROUND POWER OFF}.
 \item[\yi] Left engine RPM\dotfill\button{95\;\%}
 \item[\bi] Reft engine start button\dotfill\button{PUSH}
 \item[\gi] At 10\;\% engine RPM\dotfill\button{RIGHT THROTTLE IDLE}
 \item[\yi] Engine instruments\dotfill\button{CHECK}
 \item[\gi] After right engine at idle RPM\dotfill\button{LEFT THROTTLE IDLE}
 \item[\ri] Generator caution lights\dotfill\button{OUT}
 \item[\yi] Aux intake doors indicator\dotfill\button{OPEN}
\end{itemize}
% -------------------------------------------------------
\newpage
% Before Taxi
\begin{itemize}
 \item[] \myHead{Before Taxi}
 \item[\gi] Speed brakes\dotfill\button{RETRACT}
 \item[\gi] Flap thumb switch\dotfill\button{AUTO}
 \item[\yi] Flaps fully extended\dotfill\button{CHECK}
 \item[\mi] Damper switches\dotfill\button{YAW and PITCH}
 \item Pitch damper cutoff switch\dotfill\button{CHECK}
 \begin{itemize}
  \item[\gi] Pitch damper cutoff switch\dotfill\button{ACTUATE}
  \item[\mi] Pitch damper switch\dotfill\button{MOVES TO OFF}  
 \end{itemize}
 \item[\mi] Pitch damper switch\dotfill\button{PITCH}
 \item[\gi] Flight controls\dotfill\button{CHECK}
 \item[\gi] Pitch trim to take-off configuration\dotfill\button{$\ge$ 6}
 \item[\gi] Aileron trim\dotfill\button{CHECK and SET AS REQUIRED}
 \item[\yi] Altimeter pressure\dotfill\button{QFE}
 \item[\yi] Altimeter\dotfill\button{CHECK}
 \begin{itemize}
 \item[\yi] Mode control lever\dotfill\button{PNEU}
 \item[\yi] PNEU light\dotfill\ok{ON}
 \item[\yi] Mode control lever\dotfill\button{ELECT}
 \item[\yi] PNEU light\dotfill\ok{OFF}
 \item[\yi] Pressure difference between modes\dotfill\ok{<\;75\;ft}
 \end{itemize}
 \item[\yi] Standby attitude inicator\dotfill\button{UNCAGE}
 \item[\yi] Primary and standby attitude indicator\dotfill\button{-3\textdegree{}}
 \item Canopy lever\dotfill\button{CLOSE}
 \item[\ni] Pitot heat check\dotfill\button{ON then OFF}
 \item[\yi] Master caution light\dotfill\button{RESET}
 \item[\ri] Caution panel warning lights off\dotfill\button{CHECK}
 \item[\yi] Radar Warning Receiver\dotfill\button{POWER ON}
 \item[\mi] Radar mode selector (\rot{10 min before overheating})\dotfill\button{STBY}
 \item[\bi] Taxi lights\dotfill\button{ON}
 \item If required, tell \radio{Chief} to \radio{REMOVE the WHEEL CHOCKS}.
\end{itemize}
% --------------------------------------------------------------------------------------------
\newpage
% Taxi
\begin{itemize}
 \item[] \myHead{Taxi}
 \item Radio \radio{ATC} and \radio{REQUEST} premission to \radio{TAXI TO RUNWAY}.
 \item[\gi] Nose wheel steering\dotfill\button{ENGAGE}
 \item[\gi] Throttle setting to get rolling\dotfill\button{70\;\%}
 \item Taxi to runway at \textasciitilde\;60\;\% engine RPM.
\end{itemize}
% ---------
% Before Take-off
\begin{itemize}
 \item[] \myHead{Before Take-Off}
 \item Hold at runway line.
 \item[\yi] Pitch trim take-off configuration\dotfill\button{CHECK}
 \item[\ni] Pitot heat\dotfill\button{ON}
 \item[\ni] Engine anti-ice\dotfill\button{ON if T<4\degC}
 \item[\yi] Nose strut switch\dotfill\button{EXTEND}
 \item Radio \radio{ATC} and \radio{REQUEST} permission for \radio{TAKE-OFF}.
\end{itemize}
% \newpage
% Pitch trim table
\begin{itemize}
 \item[]
\begin{tabular}{l|l|c|c}
\hline
 \tb{Weight [lbs]}    & \tb{Configuration}                  & \tb{Pitch}    & \tb{Speed}   \\ \hline
 \mr{1}{15000}        & clean                               & \mr{1}{6}     & \mr{1}{145}  \\ \hline
 \mr{1}{15500-16000}  & ammo, missiles                      & \mr{1}{7}     & \mr{1}{155}  \\ \hline
 \mr{1}{17000-18000}  & ammo, missiles, central tank        & \mr{1}{8}     & \mr{1}{166}  \\ \hline
 \mr{1}{19000}        & ammo, missiles, 3x tank 150         & \mr{1}{7}     & \mr{1}{167}  \\ \hline
 \mr{2}{19000-21000}  & ammo, missiles. bombs,              & \mr{2}{7}     & \mr{2}{172}  \\ 
                      & rockets, central tank               &               &              \\ \hline
 \mr{1}{22000}        & ammo, missiles, 3x tank 275         & \mr{1}{7}     & \mr{1}{179}  \\ \hline
 \mr{1}{23000}        & ammo, missiles, bombs, rockets      & \mr{1}{7}     & \mr{1}{187}  \\ \hline
\end{tabular}
\end{itemize}
% -------------------------------------------------------------------------------------------------------------------
%\newpage
% Take-off
\begin{itemize}
 \item[] \myHead{Take-Off}
 \item Roll to runway centerline.
 \item Breaks\dotfill\button{HOLD}
 \item[\gi] Throttle\dotfill\button{MIL}
\begin{itemize}
 \item[\yi] Temperature\dotfill\ok{665-675\degC}
 \item[\yi] Nozzle position\dotfill\ok{0-16\;\%}
\end{itemize}
 \item[\gi] NWS button depressed and held, release breaks.
 \item[\gi] At 60\;KIAS release NWS button.
 \item[\gi] If required, throttle to full.
 \item[\gi] Rotate at \textasciitilde\;10\;KIAS before liftoff speed.
\end{itemize}
% ------------------------------------------------------------------------------------------------------------------------
\newpage
% After Take-Off
\begin{itemize}
 \item[] \myHead{After Take-Off}
 \item[\yi] Landing gear lever\dotfill\button{UP}
 \item[\gi] Pitch trim and flaps position\dotfill\button{AS REQUIRED}
 \item[\yi] Aux intake doors indicator\dotfill\ok{CLOSE}
 \item[\gi] Climb speed\dotfill\ok{>\;300\;KIAS}
 \item[\gi] Flap thumb switch\dotfill\button{AS REQUIRED}
 \item Fuel management
 \begin{itemize}
 \item[\ni] External fuel tanks: transfer swtiches\dotfill\button{ON}
 \item[\ni] No ext. fuel tanks: autobalance switch\dotfill\button{LEFT LOW}
 \end{itemize}
 \item At altitude above 8000\;ft
 \begin{itemize}
 \item[\ri] Indicated oxygen consumption\dotfill\button{CHECK}
 \item[\yi] Cockpit pressurization\dotfill\button{CHECK}
 \item[\yi] Altimeter mode\dotfill\button{AS REQUIRED}
 \end{itemize}
\end{itemize}
% ---------------------------------------------------------------------------------------------------------
\newpage
% Before Landing
\begin{itemize}
 \item[] \myHead{Before Landing}
 \item Radio \radio{ATC} for \radio{INBOUND}.
 \item[\yi] Altimeter\dotfill\button{QFE}
 \item[\ni] Fuel balancing switch\dotfill\button{CENTER}
 \item[\ni] Crossfeed switch\dotfill\button{OFF}
 \item[\yi] Hydraulic pressure\dotfill\ok{2800-3200\;PSI}
 \item[\gi] Flap lever\dotfill\button{THUMB SW}
 \item[\gi] Flap thumb switch\dotfill\button{AUTO}
\end{itemize}
% \newpage
% Landing approach
\begin{itemize}
 \item[] \myHead{Landing}
 \item Radio \radio{ATC} and \radio{REQUEST LANDING}.
 \item[] \tb{Upwind leg:}
 \item Enter traffic pattern at 300 KIAS.
 \item Descend to 1500\;ft AGL 3 miles before end of runway.
 \item[] \tb{Crosswind leg:}
 \item Maintain 1500\;ft AGL
 \item[] \tb{Downwind leg:}
 \item[\yi] Landing gear lever (\warn{<260 KIAS})\dotfill\button{DOWN}
 \item[\yi] Gear indicator lights\dotfill\ok{GREEN}
 \item[\gi] Speed brake\dotfill\button{AS REQUIRED}
 \item[] \tb{Base leg:}
 \item Decelecate to \textasciitilde165 KIAS and keep altitude of 1500\;ft.
 \item[\oi] AOA indexer\dotfill\ok{ON SPEED}
 \item[] \tb{Final approach:}
 \item Decent rate \textasciitilde1000\;ft/min.
 \item Decrease speed to 145 KIAS.
 \item[\oi] AOA indexer\dotfill\ok{ON SPEED}
 \item Approaching runway decrease vertical speed to 400\;ft/min.
 \item Flare at \textasciitilde20\;ft and smoothly decrease speed to idle.
 \item Touchdown at 135 KIAS.
 \item[\yi] Deploy drag chute and carefully apply wheel breaks.
\end{itemize}
% ---------------------------------------------------------------------------------------
\newpage
% After Landing
\begin{itemize}
 % After landing
 \item[] \myHead{After Landing}
 \item[\yi] Jettison drag chute.
 \item[\ni] Cockpit pressurization switch\dotfill\button{RAM DUMP}
 \item[\gi] Flap thumb switch\dotfill\button{UP}
 \item[\gi] Speed brake\dotfill\button{OUT}
 \item[\mi] Radar mode selector\dotfill\button{OFF}
 \item[\oi] Optical sight mode selector\dotfill\button{OFF}
 \item[\ni] Pitot heat and engine anti-ice switches\dotfill\button{OFF}
\end{itemize}
%\newpage
%  % Engine shutdown
\begin{itemize}
 \item[] \myHead{Engine Shutdown}
 \item[\ni] Cockpit pressurization switch\dotfill\button{RAM DUMP}
 \item Canopy\dotfill\button{OPEN}
 \item[\ri] Cockpit pressurization switch\dotfill\button{NORMAL/CABIN PRESS}
 \item All unguarded switches (except batt, gen, boos pumps)\dotfill\button{OFF}
 \item[\gi] Throttles\dotfill\button{OFF}
 \item[\yi] Standby attitude indicator\dotfill\button{CAGE and LOCK}
 \item[\ni] Generator switches\dotfill\button{OFF}
 \item[\ni] Boost pump switches\dotfill\button{OFF}
 \item[\ni] Battery switch\dotfill\button{OFF}
\end{itemize}
%---------------------------------------------------------------------------
\newpage
% Air-to-Ground: Guns & Rockets
\begin{itemize}
 \item[] \myHead{Air-to-Ground:\;Gun\;\&\;Rockets}
 \item[\bi] Weapon switch\dotfill\button{GUNS MSL \& CAMR}
 \item[\oi] Sight mode selector\dotfill\button{MAN}
 \item[\oi] Reticule depression knob\dotfill\button{SET}
 \item Rocket employment:
 \begin{itemize}
   \item[\bi] External stores switch\dotfill\button{RKT/DISP}
   \item[\bi] Pylons with LAU\dotfill\button{ON}
 \end{itemize}
 \item Climb to initial altitude (5000-6000 ft AGL).
 \item Adjust initial speed (350-370 knots).
 \item Set target up at 10 o'clock and roll-in when ready.
 \item Align sight pipper with target.
 \item Watch dive angle and speed.
 \item At release altitude
 \begin{itemize}
  \item[\gi] Guns: pull trigger to second detent
  \item[\gi] Rockets: press bomb-rocket release button.
 \end{itemize}
\item Perform 4G pullout within 2 seconds.
\end{itemize}
\vspace{1em}
%\newpage
% Air-to-Ground Guns Table
\begin{itemize}
 \item[] \myHead{Guns Table}
 \item[]
\begin{tabular}{c|c|c|c|c|c}
\hline
 Dive   & \mcl{2}{\ok{Initial}} & \mcl{2}{\warn{Release}} & Reticule\\
 Angle  & Altitude & Speed   & Altitude & Speed   & Depression\\ \hline
\tb{20} & 5000     & 350-370 & 2000     & 400     & 12        \\ \hline
\tb{30} & 6000     & 350-370 & 3000     & 400     & 8         \\ \hline
\end{tabular}
\end{itemize}
\vspace{1em}
\begin{itemize}
 \item[]\myHead{Rockets Table}
 \item[]
%\newpage
% Air-to-Ground Rockets
\begin{tabular}{c|c|c|c|c|c|c}
\hline
 Dive           & \mcl{2}{\ok{Initial}}          & \mcl{2}{\warn{Release}}    & Reticule   & Rocket \\
 Angle          & Alt     & Speed           & Alt     & Speed       & Depression & Type   \\ \hline
\mr{2}{\tb{20}} & \mr{2}{5000} & \mr{2}{350-370} & \mr{2}{1500} & \mr{2}{400} & 14         & HYDRA  \\ \cline{6-7}
                &              &                 &              &             & 34         & FFAR   \\ \hline
\mr{2}{\tb{30}} & \mr{2}{6000} & \mr{2}{350}     & \mr{2}{2000} & \mr{2}{400} & 10         & HYDRA  \\ \cline{6-7}
                &              &                 &              &             & 30         & FFAR   \\ \hline
\end{tabular}
\end{itemize}
% -------------------------------------------------------------------------------
\newpage
% Air-to-Ground: Bombs
\begin{itemize}
 \item[]\myHead{Air-to-Grund:\;Bombs}
 \item[\bi] Weapon switch\dotfill\button{GUNS MSL \& CAMR}
 \item[\oi] Sight mode selector\dotfill\button{MAN}
 \item[\oi] Reticule depression knob\dotfill\button{SET}
 \item[\bi] External stores switch\dotfill\button{BOMB or RIPL}
 \item[\bi] If riple release, INTERVAL switch\dotfill\button{AS REQUIRED}
 \item[\bi] Pylons with bombs loaded\dotfill\button{ON}
 \item Climb to initial altitude (5000-6000 ft AGL).
 \item Adjust initial speed to 350 knots.
 \item Set target up at 10 o'clock and roll-in when ready.
 \item Align sight pipper with target.
 \item Watch dive angle and speed.
 \item[\gi] At release altitude press bomb-rocket release button.
 \item Perform 4G pullout within 2 seconds.
\end{itemize}
\vspace{1em}
% Dive Bombing Table
\begin{itemize}
 \item[]\myHead{Bombs Table}
 \item[]
\begin{tabular}{c|c|c|c|c|c}
\hline
 Dive   & \mcl{2}{\ok{Initial}} & \mcl{2}{\warn{Release}} & Reticule\\
 Angle  & Altitude & Speed & Altitude & Speed   & Depression\\ \hline
\tb{20} & 5000     & 350   & 1500     & 380-400 & 80        \\ \hline
\tb{30} & 6000     & 350   & 2000     & 440-450 & 79        \\ \hline
\end{tabular}
\end{itemize}
% ---------------------------------------------------------------------------------
\newpage
% Air-to-Air: Missiles
\begin{itemize}
 \item[] \myHead{Air-to-Air:\;Missiles}
 \item[\bi] Weapon switch\dotfill\button{GUNS MSL \& CAMR}
 \item[\oi] Sight mode selector\dotfill\button{MSL}
 \item[\bi] Armament panel outer pylon switches\dotfill\button{UP}
 \item[\mi] Radar mode selector\dotfill\button{OPER}
 \item[\gi] Radar range selector - \warn{MSL} or \ok{DM}\dotfill\button{\warn{40} or \ok{10}}
 \item[\gi] Radar elevation antenna\dotfill\button{AS REQUIRED}
 \item Align target to horizontal center of the radar display.
 \item \warn{MSL} Mode
 \begin{itemize}
 \item TDC on target icon and lock with ACQ button.
  \end{itemize}
  \item[\gi] \ok{DM} Mode
 \begin{itemize}
 \item[\gi] 5 NM from target, DOGFIGHT/RESUME switch forward.
 %\item[] Missile will lock the nearest target
  \end{itemize}
 \item[\yi] When in range, LK ON light and IN RANGE light illumiate.
 \item[] Red dot appears next to gunsight reticle.
 \item[\gi] Press weapon release button to fire.
 %\item[] Unlock/abort
 \item[\gi] Unlock target by DOGFIGHT/RESUME CENTER-PRESS.
 \item[\gi] Abort by pressing the MISSILE UNCAGE switch.
\end{itemize}
% ------------------------------------------------------------------------------------
\vspace{0.5em}
% Air-to-Air: Guns
\begin{itemize}
 \item[] \myHead{Air-to-Air:\;Guns}
 \item[\bi] Weapon switch\dotfill\button{GUNS MSL \& CAMR}
 \item[\oi] Sight mode selector\dotfill\button{A/A1 or A/A2}
 \item[\mi] Radar mode selector\dotfill\button{OPER}
 \item[\gi] Radar range selector\dotfill\button{10}
 \item[\gi] Radar elevation antenna\dotfill\button{AS REQUIRED}
 \item Align target to horizontal center of the radar display.
 \item[\gi] 1 NM from target engage DG mode by DOGFIGHT/RESUME aft.
 %\item[] Radar will automatically lock the nearest target.
 \item[\yi] When in range, LK ON light and IN RANGE light illumiate.
 \item[] Red dot appears next to gunsight reticle.
 \item[\gi] Press trigger to second detent to fire.
 %\item Unlock target by DOGFIGHT/RESUME CENTER-PRESS.
\end{itemize}
% -----------------------------------------------------------
}
\end{document}
% ---------------------------------------------------------------------------------------------------